---
title: "anm332_GloVe_methodstutorial_04.14.21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


https://quanteda.io/articles/pkgdown/replication/text2vec.html


Library the necessary packages
```{r}
library(quanteda)
library(devtools)# get devtools to install quanteda.corpora
#devtools::install_github("quanteda/quanteda.corpora")
#install.packages("quanteda.textstats")
library(quanteda.textstats)
library(quanteda.corpora)
library(tidytext)
library(tm)
```

Read in the data, clean, preprocess, create matrix and corpus
```{r}
# Read in the data: ####################################################################### 

# terrorism data: 
ter_df <- read.csv("/Users/amandamoeller/Desktop/PLSC 597 ML/Methods Tutorial.nosync/only_tertext_data.csv")
ter_df$rawtext <- ter_df$Text..raw.data. # change name of text variable

# non-terrorism data: 
nonter_df <- read.csv("/Users/amandamoeller/Desktop/PLSC 597 ML/Methods Tutorial.nosync/only_nontertext_data.csv")


# clean up both sets of data (normalization): ############################################
ter_df$rawtext <- tolower(ter_df$rawtext)
ter_df$rawtext <- removeNumbers(ter_df$rawtext)
ter_df$rawtext <- removePunctuation(ter_df$rawtext)
# removeWords(ter_df$rawtext, stopwords("english")) # this didn't work?
tokens_remove(tokens(ter_df$rawtext, remove_punct = TRUE), stopwords("english")) #ok this worked

nonter_df$rawtext <- tolower(nonter_df$rawtext)
nonter_df$rawtext <- removeNumbers(nonter_df$rawtext)
nonter_df$rawtext <- removePunctuation(nonter_df$rawtext)
# removeWords(ter_df$rawtext, stopwords("english")) # this didn't work?
tokens_remove(tokens(nonter_df$rawtext, remove_punct = TRUE), stopwords("english")) #ok this worked



# Create the corpus and matrices for terrorism and non-terrorism data: ################################## 

# 1) terrorism corpus, matrix
ter_corp <- corpus(ter_df, text_field="rawtext")
ter_dfm <- dfm(ter_corp, remove_punct = TRUE, remove = stopwords('en')) # for example, stop words are still in here???
ter_dfm # here's the terrorism corpus

ter_corp_matrix <- as.matrix(ter_corp) # here's the terrorism corpus as a matrix
ter_corp_df <- data.frame(text = sapply(ter_corp, as.character), stringsAsFactors = FALSE) # here's the terrorism corpus as a df

# 2) non-terrorism corpus, matrix
nonter_corp <- corpus(nonter_df, text_field="rawtext")
nonter_dfm <- dfm(nonter_corp, remove_punct = TRUE, remove = stopwords('en'))
nonter_dfm

nonter_corp_matrix <- as.matrix(nonter_corp)
nonter_corp_df <- data.frame(text = sapply(nonter_corp, as.character), stringsAsFactors = FALSE)
```

Tokenize the corpus and then get the names of the features that occur 5+ times. Trimming the features before constructing the fcm:
```{r}
#wiki_toks <- tokens(wiki_corp)
#feats <- dfm(wiki_toks, verbose = TRUE) %>%
    #dfm_trim(min_termfreq = 5) %>%
    #featnames()

########## for terrorism:

ter_toks <- tokens(ter_corp)
t_feats <- dfm(ter_toks, verbose = TRUE) %>%
    dfm_trim(min_termfreq = 5) %>%
    featnames()

t_feats

########## for non-terrorism:
nonter_toks <- tokens(nonter_corp)
nt_feats <- dfm(nonter_toks, verbose = TRUE) %>%
    dfm_trim(min_termfreq = 5) %>%
    featnames()

nt_feats
```
Creating a dfm from a tokens input...
 ...lowercasing
 ...found 151 documents, 7,764 features
 ...complete, elapsed time: 0.048 seconds.
Finished constructing a 151 x 7,764 sparse dfm.


Leave the pads so that non-adjacent words will not become adjacent
Not sure if this is necessary? But basically just replaces empty strings if tokens are removed later
```{r}
ter_toks <- tokens_select(ter_toks, t_feats, padding = TRUE)
ter_toks

nonter_toks <- tokens_select(nonter_toks, nt_feats, padding = TRUE)
nonter_toks
```

Construct the feature co-occurrence matrix
```{r}
# terrorism:
ter_fcm <- fcm(ter_toks, context = "window", count = "weighted", weights = 1 / (1:5), tri = TRUE)
ter_fcm

# non-terrorism:
nonter_fcm <- fcm(nonter_toks, context = "window", count = "weighted", weights = 1 / (1:5), tri = TRUE)
nonter_fcm

# looks like stop words are still in it. the, to, of, etc. Need to figure out how to remove those 
```

Fit word embedding model
Fit the GloVe model using rsparse.
```{r}
library(text2vec)

# ter:
ter_glove <- GlobalVectors$new(rank = 50, x_max = 10)
ter_wv_main <- ter_glove$fit_transform(ter_fcm, n_iter = 10,
                               convergence_tol = 0.01, n_threads = 8)

dim(ter_wv_main)
ter_wv_main

# nnon-ter:
nonter_glove <- GlobalVectors$new(rank = 50, x_max = 10)
nonter_wv_main <- nonter_glove$fit_transform(nonter_fcm, n_iter = 10,
                               convergence_tol = 0.01, n_threads = 8)

dim(nonter_wv_main)
nonter_wv_main
```
INFO  [23:30:41.506] epoch 10, loss 0.0212 (terrorism)
INFO  [10:43:50.439] epoch 10, loss 0.0330 (non-terrorism)


"Averaging learned word vectors
The two vectors are main and context. According to the Glove paper, averaging the two word vectors results in more accurate representation."
```{r}
# t:
ter_wv_context <- ter_glove$components
dim(ter_wv_context)
## [1]    50 2082
ter_word_vectors <- ter_wv_main + t(ter_wv_context)
ter_word_vectors

# nt:
nonter_wv_context <- nonter_glove$components
dim(nonter_wv_context)
## 50 929
nonter_word_vectors <- nonter_wv_main + t(nonter_wv_context)
nonter_word_vectors
```


Examining term representations
Aka we're finding word vectors that are the most similar to each other
```{r}
library(quanteda.textstats)

# I'm most interested in looking at "power", "fighting", "movement"
# (THESE ARE COMMON TO BOTH TER AND NON-TER DOCUMENTS AND USED 10+ TIMES IN BOTH CORPUSES -- this is discovered later in the code, I just need to reorganize the code later)


#Terrorism and POWER: ##########################################################
ter_pow <- ter_word_vectors["power", , drop=FALSE]

terpow_cos_sim <- textstat_simil(x=as.dfm(ter_word_vectors), y=as.dfm(ter_pow),
                          method="cosine")
head(sort(terpow_cos_sim[, 1], decreasing = TRUE), 10)
#     power       our  interest   victims     since   culture    simple     faith      this  religion 
# 1.0000000 0.4186855 0.3717540 0.3601933 0.3539113 0.3503652 0.3448984 0.3350568 0.3218579 0.3166358 

# Non-terrorism and POWER:
nonter_pow <- nonter_word_vectors["power", , drop=FALSE]

nonterpow_cos_sim <- textstat_simil(x=as.dfm(nonter_word_vectors), y=as.dfm(nonter_pow),
                          method="cosine")
head(sort(nonterpow_cos_sim[, 1], decreasing = TRUE), 10)
#  power            my         march      prasadam      together         right           its revolutionary       protect 
# 1.0000000     0.5043184     0.4761917     0.4500863     0.4411783     0.4327637     0.4314553     0.4016746     0.3831767 
#         work 
#    0.3691006 



#Terrorism and FIGHTING: ##########################################################
ter_fighting <- ter_word_vectors["fighting", , drop=FALSE]

terfighting_cos_sim <- textstat_simil(x=as.dfm(ter_word_vectors), y=as.dfm(ter_fighting),
                          method="cosine")
head(sort(terfighting_cos_sim[, 1], decreasing = TRUE), 10)
# fighting       them       sons      those supporting      allah     become      islÄm        all  peninsula 
# 1.0000000  0.5288757  0.4493841  0.4266149  0.4172160  0.4110513  0.3817323  0.3709447  0.3629710  0.3623832 


# Non-terrorism and FIGHTING:
nonter_fighting <- nonter_word_vectors["fighting", , drop=FALSE]

nonterfighting_cos_sim <- textstat_simil(x=as.dfm(nonter_word_vectors), y=as.dfm(nonter_fighting),
                          method="cosine")
head(sort(nonterfighting_cos_sim[, 1], decreasing = TRUE), 10)
# fighting          im   including   achieving  principles     restore       point       least     methods afghanistan 
# 1.0000000   0.5389822   0.4579108   0.4116088   0.4005523   0.3992339   0.3971297   0.3969467   0.3901475   0.3886486 


#Terrorism and movement: ##########################################################
ter_movement <- ter_word_vectors["movement", , drop=FALSE]

termovement_cos_sim <- textstat_simil(x=as.dfm(ter_word_vectors), y=as.dfm(ter_movement),
                          method="cosine")
head(sort(termovement_cos_sim[, 1], decreasing = TRUE), 10)
# movement environmental        reform         black       support        animal        rights          jews           for 
# 1.0000000     0.5020501     0.4965203     0.4597535     0.4431389     0.4205784     0.4059399     0.3860838     0.3834980 
#         harm 
#    0.3753824 

# Non-terrorism and MOVEMENT:
nonter_movement <- nonter_word_vectors["movement", , drop=FALSE]

nontermovement_cos_sim <- textstat_simil(x=as.dfm(nonter_word_vectors), y=as.dfm(nonter_movement),
                          method="cosine")
head(sort(nontermovement_cos_sim[, 1], decreasing = TRUE), 10)
#movement    should      back      have      been      will    around        we therefore        be 
# 1.0000000 0.4338365 0.4009519 0.3563422 0.3516061 0.3502377 0.3359636 0.3346836 0.3306835 0.3213814 

```

Plot word embeddings in 2d space:
```{r}
#install.packages("irlba")
library(irlba)

ter_svd <- irlba(ter_dfm, 2, maxit=500)

#next we output the word vectors:
ter_word_vectors <- ter_svd$u
rownames(ter_word_vectors) <- rownames(ter_dfm)


# use ter_wv_main and nonter_wv_main vectors instead

#terrorism:

#grab 50 words
ter_forplot<-as.data.frame(ter_wv_main[50:100,])
ter_forplot$word<-rownames(ter_forplot)

#now plot
library(ggplot2)
ggplot(ter_forplot, aes(x=V1, y=V2, label=word))+
  geom_text(aes(label=word),hjust=0, vjust=0, color="blue")+
  theme_minimal()+
  xlab("First Dimension Created by GloVe")+
  ylab("Second Dimension Created by GloVe")


# nnon-terrorism:

#grab 50 words
nonter_forplot<-as.data.frame(nonter_wv_main[50:100,])
nonter_forplot$word<-rownames(nonter_forplot)

#now plot
library(ggplot2)
ggplot(nonter_forplot, aes(x=V1, y=V2, label=word))+
  geom_text(aes(label=word),hjust=0, vjust=0, color="blue")+
  theme_minimal()+
  xlab("First Dimension Created by GloVe")+
  ylab("Second Dimension Created by GloVe")
```


DOCUMENT FREQUENCY MATRICES BELOW
```{r}
library(gdata)

# 1) Terrorism dfm:

# dfm = document-feature matrix
t_dfm <- dfm(ter_corp, ignoredFeatures = stopwords("english"), stem = TRUE)

t_dfm <- trim(t_dfm, minDoc = minDoc, minCount = minCount)
t_dfm

plotDFM <- function(t_dfm)
t_dfm_plot <- plot(t_dfm)


# 2) Non-terrorism dfm:
nt_dfm <- dfm(nonter_corp, ignoredFeatures = stopwords("english"), stem = TRUE)

nt_dfm <- trim(nt_dfm, minDoc = minDoc, minCount = minCount)
nt_dfm

plotDFM2 <- function(nt_dfm)
nt_dfm_plot <- plot(nt_dfm)


```

NOW GENERATE FREQUENT TERMS IN T AND NT TDM (term doc matrix)
```{r}

## tokenize text in dfs:
library(tokenizers)

ter_df$ttokens <- tokenize_words(ter_df$rawtext)
ttokens <- tokenize_words(ter_df$rawtext)

nonter_df$ntokens <- tokenize_words(nonter_df$rawtext)
ntokens <- tokenize_words(nonter_df$rawtext)


##### create terrorism TDM (term doc matrix):

## 1: df to corpus
corp_ter <- VCorpus(VectorSource(ter_df$ttokens))

## 2: corpus to tdm
t_tdm <- TermDocumentMatrix(corp_ter)

## 3: findFreqTerms(tdm)
findFreqTerms(t_tdm, lowfreq=10, highfreq=Inf)


##### create non-terrorism TDM (term doc matrix):

## 1: df to corpus
corp_nt <- VCorpus(VectorSource(nonter_df$ntokens)) 

## 2: corpus to tdm
nt_tdm <- TermDocumentMatrix(corp_nt)

## 3: findFreqTerms(tdm)
findFreqTerms(nt_tdm, lowfreq=10, highfreq=Inf)



### COMMON WORDS:
# American, believe, country, fighting, government/s, good, religion, world, action, economic, human, media, movement, nation, power, rights, support, violent, 


# I'm most interested in looking at "power", "fighting", "movement"

```


WHAT I NEED HELP WITH: 
- removing stopwords and stemming (I did this in the code early on, but it didn't seem to actually remove all the stop words)
- plot word embeddings of target words (visualize findings from lines 170-241)


